Viscous Erosion in Porous Media

### 2018-03-29 docs/methods/erosion_methods.tex
NM

	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations. Loosely, with $N_\iin = 1024$ fixed, the values 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively. As seen in the table, both the aspect ratio and the opening angle converge as $\eps, \sigma \to 0$ with roughly first order. To quantify the uncertainty involved in our angle measurement procedure, we show the estimated uncertainty, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation point....

@@

%We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal. 
%Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively. 
%As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$. We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit. As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.

>>>>

	To more thoroughly examine the influence of the smoothing parameters, we report in Table~\ref{table:arangle} the long-time values of the aspect ratio and opening angle for each of the three simulations. Loosely speaking, since $N_\iin = 1024$ is fixed, the values $\eps = \sigma = $ 20/1024, 10/1024, and 5/1024 correspond to smoothing over the nearest 20, 10, and 5 grid points respectively. The table shows that both the aspect ratio and opening angle converge with roughly first-order as $\eps, \sigma \to 0$. In addition, we show an estimate of the uncertainty involved in our angle measurement, which is obtained by varying the degree of the fitting polynomial and the size of the excluded region around the stagnation points. The estimates show that as $\eps, \sigma \to 0$ the angle-measurements become more precise and converge to the predicted value of $102^{\circ}$.

@@
